European or American? A re-examination of the transatlantic influence over the IMF

### 2025-04-22 demo/demo.qmd
comment out subtitle
fix demo paths (#3)

---
title: European or American? A re-examination of the transatlantic influence over the IMF
subtitle: GV499 Dissertation
header-includes: |
  \AtBeginDocument{\title[GV499 Dissertation]{European or American? A re-examination of the transatlantic influence over the IMF}}
date: last-modified
author: Dianyi Yang
format:
  beamer:
    theme: Madrid
bibliography: references.bib
csl: extra/apa.csl
project:
  execute-dir: "D:/OneDrive - London School of Economics/Desktop/GV499/IMF"
---

@@

```{r setup}
knitr::opts_knit$set(root.dir = 'D:/OneDrive - London School of Economics/Desktop/GV499/IMF')
need <- c('tidyverse','haven','AER','fixest','modelsummary',
          'corrplot', 'kableExtra','car','parameters') # list packages needed
have <- need %in% rownames(installed.packages()) # checks packages you have
if(any(!have)) install.packages(need[!have]) # install missing packages
invisible(lapply(need, library, character.only=T))
```

```{r results}
load('save/regtable.RData')

@@

coefmap <- c('us' = 'US Influence',
             'eu' = 'EU Influence',
             'imf' = 'IMF Influence',
             'lnrgdpnew' = 'GDP',
             'lnrgdpnewsq' = 'GDP$^2$',
             'rgdpchnew' = 'GDPpc',
             'rgdpchnewsquare' = "GDPpc$^2$",
             'growth1new' = 'GDPpc growth',
             'reserv1' = 'Reserves',
             'oecd1' = 'OECD',
              '(Intercept)' = '(Intercept)')
gof_map <- list(list("raw" = "equality", "clean" = "US=EU", "fmt" = NULL),
                list("raw" = "nobs", "clean" = "$N$", "fmt" = 0),
                list('raw' = 'vcov.type', 'clean' = 'Std.Errors', 'fmt' = NULL))
msummary(regtable, coef_map=coefmap, gof_map=gof_map, stars=T, escape=F) %>% 
  kable_styling(latex_options="scale_down")
```

>>>>

---
title: European or American? A re-examination of the transatlantic influence over the IMF
# subtitle: GV499 Dissertation
header-includes: |
  \AtBeginDocument{\title[GV499 Dissertation]{European or American? A re-examination of the transatlantic influence over the IMF}}
date: last-modified
author: Dianyi Yang
format:
  beamer:
    theme: Madrid
bibliography: references.bib
csl: extra/apa.csl
project:
  execute-dir: "D:/OneDrive - London School of Economics/Desktop/GV499/IMF"
---

@@

```{r setup}
need <- c('tidyverse','haven','AER','fixest','modelsummary',
          'corrplot', 'kableExtra','car','parameters') # list packages needed
have <- need %in% rownames(installed.packages()) # checks packages you have
if(any(!have)) install.packages(need[!have]) # install missing packages
invisible(lapply(need, library, character.only=T))
```

```{r results}
load('../save/regtable.RData')

@@

coefmap <- c('us' = 'US Influence',
             'eu' = 'EU Influence',
             'imf' = 'IMF Influence',
             'lnrgdpnew' = 'GDP',
             'lnrgdpnewsq' = 'GDP$^2$',
             'rgdpchnew' = 'GDPpc',
             'rgdpchnewsquare' = "GDPpc$^2$",
             'growth1new' = 'GDPpc growth',
             'reserv1' = 'Reserves',
             'oecd1' = 'OECD',
              '(Intercept)' = '(Intercept)')
gof_map <- list(list("raw" = "equality", "clean" = "US=EU", "fmt" = NULL),
                list("raw" = "nobs", "clean" = "$N$", "fmt" = 0),
                list('raw' = 'vcov.type', 'clean' = 'Std.Errors', 'fmt' = NULL))
msummary(regtable, coef_map=coefmap, gof_map=gof_map, stars=T, escape=F, output = "kableExtra") %>% 
  kable_styling(latex_options="scale_down")
```
